Calculating life expectancy and exploring missingness

### 2016-10-25 Code/1_Explore_Data_v2.Rmd

>>>>

```{r calculate_cod_decomp}
#still need to convince myself this works
list.cod.decomp.tables <- vector(mode = "list", length = dim(paired.ids)[1])

  if(length(white.index) != 0 & length(black.index) != 0) {
    ct.white <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexWhite"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop2 = cod_prop_death5)

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop1 = cod_prop_death5)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2"))

    list.cod.decomp.tables[[i]] <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]), 
                                                 life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                 decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                 cod.table = ct.both, "Age2", "COD2", "prop1", "prop2")
  } else {
    list.cod.decomp.tables[[i]] <- "Couldn't compare life tables"
  }  
  print(i)
}
